---
title: "Close the Gap #5: Geodata - Classification"
output: html_notebook
---

> TODO: Sources - FixMyBerlin, Uber, Luftdaten.info, CityLab

## Classification of Segements

> Index levels for demo
  
  + accident: -3
  + air quality: -2
  + traffic probe: -1

### Intersect with Accident Data

> if intersection -> assign severity level 3, else 0

```{r eval=FALSE, include=FALSE, echo=FALSE}
load(file ="outputs/data_close_gap_raw.RData") # returns close_gap
```


```{r}
close_gap <- close_gap %>% 
  mutate(accident = ifelse(lengths(st_intersects(geometry, unfaelle_buffer)) >= 1, 3, 0 )) %>% 
  select(accident, everything())
```

### Intersect with Air Quality Data

> if intersection -> assign severity level 2, else 0

```{r}
close_gap <- close_gap %>% 
  mutate(airquality = ifelse(lengths(st_intersects(geometry, luftdaten_berlin_buffer)) >= 1, 2, 0 )) %>%
  select(airquality, everything())
```


### Spatial (Left) Join with Uber Data

> DUMMY: if intersection -> assign severity level 1, else 0
> for production, segmentize Uber segements and bike lane segments (i.e. 50m units) to increase precision and reduce redundancy

```{r}
close_gap <- close_gap %>% 
  st_join(y = uber_06_berlin, left = TRUE) %>% 
  mutate(probe = ifelse(speed_mean_kph < 15, 1, 0)) 
```

### Calculate Segment Index

> Demo Formula

```{r}
close_gap <- close_gap %>% 
  mutate(index = (accident + airquality + probe) * -1) %>% 
  select(index, everything())
```

## Final Geojson for Demo

> further reducing subset to relieve frontend for demo

```{r}
# close_gap <- close_gap %>% filter(happy_bike_index < 3)
# save(close_gapbase, file = "outputs/final_full.RData")
```

> subsetting into HappyBike Layer & Index Layer

```{r}
close_gapbase <- close_gap %>% filter(is.na(index))
# save(close_gapbase, file = "outputs/final_full_base.RData")
```

```{r}
close_gapindex <- close_gap %>% filter(!is.na(index))
# save(close_gapindex, file = "outputs/final_full_index.RData")
```

## Short Analysis: Length of Bad Lanes

> UNVETTED / NOT DOUBLE-CHECKED; Just to demonstrate feasibility

> (Un)HappyBike Segments (in km) (for Level < 6)

```{r}
close_gapbase %>% 
  summarise(n = n(), total_length_base_km = sum(length_m)/1000,
            avg_length_km = total_length_base_km/n)
```

> Index Segments (in km) (for Level < 6)

```{r}
close_gapindex %>% 
  summarise(n = n(),
            total_length_index_km = sum(length_m)/1000,
            avg_length_km = total_length_index_km/n)
```

## Geojson Files for Demo

> base layer

```{r}
geojsonio::geojson_write(close_gapbase, file = "outputs/final_full_base.geojson", encoding = "UTF-8")
```

> index layer

```{r}
geojsonio::geojson_write(close_gapindex, file = "outputs/final_full_index.geojson", encoding = "UTF-8")
```

